Supplementary Material for the Paper ``Enriching Object Detection with\\2D-3D Registration and Continuous Viewpoint Estimation''

### 2014-11-20 egpaper_supp.tex
pass over suppl

%%%%%%%%% BODY TEXT
We present qualitative results in the supplementary material for our paper
``Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint
Estimation''.
% In Sect.~\ref{sec:3dobject}, we present detection result on qualitative results.

\section{3D Object Dataset}
\label{sect:3dobject}

It this section, we provide qualitative examples and plots for the experiment
``2D-3D Matching as an Object Detector''. To recapitulate, we run our ensemble
of NZ-WHO templates as an ensemble of exemplar templates on 3D Object
dataset\cite{savarese07} without fine-tuning stage. The detection average
precision, average viewpoint precision, viewpoint confusion matrix and mean
precision in pose estimation results are on Fig.~\ref{fig:3dobject_ap}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.99\linewidth]{supp/car_ap_3dobject_tight.png}\\
  \vspace{-5pt}
    (a) Car\\
  \includegraphics[width=0.99\linewidth]{supp/bicycle_ap_3dobject_tight.png}\\
  \vspace{-5pt}
    (b) Bicycle\\
  \caption{Detection and pose estimation on 3D Object dataset car category (top) and bicycle category (bottom).
  Average Precision (red) and Average Viewpoint Precision (green) are overlaid on the left plot and
  viewpoint confusion table and MPPE are on the right plot. The viewpoint index 1 is front, index 2 is
  front-right, \dots index 8 is front-left.}
  \label{fig:3dobject_ap}
\end{figure}

For qualitative results, we put successful car viewpoint prediction results on
Fig.~\ref{fig:3dobject_car_good} and
failure cases on Fig.~\ref{fig:3dobject_car_bad}. And for bicycle, successful
results are on Fig.~\ref{fig:3dobject_bicycle_good} and
failure cases on Fig.~\ref{fig:3dobject_bicycle_bad}. We followed detection
and viewpoint estimation criteria of \cite{Xiang12} where detection is correct
iff intersection over union of more than 0.5 and viewpoint estimation is
correct iff detection is correct \emph{and} azimuth of the viewpoint
prediction falls in to the correct viewpoint bin.

>>>>

%%%%%%%%% BODY TEXT
In the following, we present additional quantitative and qualitative
results that accompany the experiments described in Sect.~6 of the
main paper, ``Enriching Object Detection with 2D-3D Registration and
Continuous Viewpoint Estimation''.
% In Sect.~\ref{sec:3dobject}, we present detection result on qualitative results.

\section{2D-3D Matching as an Object Detector}
\label{sect:3dobject}
It this section, we provide qualitative examples and plots for the experiment
``2D-3D Matching as an Object Detector'' (Sect.~6.2 in the main
paper).

To recapitulate, we run our ensemble
of NZ-WHO templates on the 3D Object Classes
dataset~\cite{savarese07}, without the fine-tuning
stage. Fig.~\ref{fig:3dobject_ap} gives the corresponding detection
average precision, average viewpoint precision, viewpoint confusion
matrix and mean precision in pose estimation results. Specifically, we
followed the detection and viewpoint estimation criteria
of~\cite{Xiang12} where a detection is correct iff
intersection over union is at least $0.5$ and viewpoint estimation is
correct iff detection is correct \emph{and} azimuth of the viewpoint
prediction falls into the correct viewpoint bin.
%
\begin{figure}[h]
  \centering
  \includegraphics[width=0.99\linewidth]{supp/car_ap_3dobject_tight.png}\\
  \vspace{-5pt}
    (a) Car\\
  \includegraphics[width=0.99\linewidth]{supp/bicycle_ap_3dobject_tight.png}\\
  \vspace{-5pt}
    (b) Bicycle\\
  \caption{Detection and pose estimation on 3D Object
    Classes~\cite{savarese07} car (a) and bicycle (b).
    Average Precision (red) and Average Viewpoint Precision (green)
    are given in the left plot and viewpoint confusion table and MPPE
    are given in the right plot. The viewpoint index 1 is front, 2 is
    front-right, \dots, 8 is front-left.}
  \label{fig:3dobject_ap}
\end{figure}

Fig.~\ref{fig:3dobject_car_good} shows successful detection and
viewpoint estimation results for car,
Fig.~\ref{fig:3dobject_bicycle_good} for
bicycle. Fig.~\ref{fig:3dobject_car_bad} and
Fig.~\ref{fig:3dobject_bicycle_bad} show failure cases, which are
mostly due to confused front and back views for cars, and slanted
bicycle poses.
